Challenges in Developing Great Quasi-Monte Carlo Software

### 2023-02-11 MCQMC2022ChallengesQMCSoftwareArticle.tex
2023 Mac 14 Updates

%%%%Fred start
\include{common-macros.tex}
\usepackage{cite}
\usepackage{xspace}
\usepackage[hyphens]{url}
\providecommand{\HickernellFJ}{Hickernell\xspace}

@@

LD generators are the most prevalent generally available components of QMC software.  These generators appear in Association of Computing Machinery  publications \cite{BraFox88,BraFoxNie92,HonHic00a}, FinDer \cite{PasTra95,FinDer}, libseq \cite{FriKel02,FriKelweb}, BRODA \cite{BRODA20a}, NAG \cite{NAG27}, MATLAB \cite{MAT9.13}, SamplePack \cite{SamplePack}, Gr\"nschlo{\ss}'s website \cite{GruWeb}, the Magic Point Shop \cite{NuyWeb}, Julia \cite{QMCJulia}, SciPy \cite{virtanen2020scipy}, PyTorch \cite{paszke2019pytorch}, and TensorFlow \cite{tfqfQMC2021a}, and MatBuilder \cite{paulin2022}.  Joe and Kuo

@@

R by Lemieux

>>>>

%%%%Fred start
\input{common-macros.tex}
\usepackage{cite}
\usepackage{xspace}
\usepackage[hyphens]{url}
\providecommand{\HickernellFJ}{Hickernell\xspace}

@@

LD generators are the most prevalent generally available components of QMC software.  These generators appear in Association of Computing Machinery  publications \cite{BraFox88,BraFoxNie92,HonHic00a}, FinDer \cite{PasTra95,FinDer}, libseq \cite{FriKel02,FriKelweb}, BRODA \cite{BRODA20a}, NAG \cite{NAG27}, MATLAB \cite{MAT9.13}, SamplePack \cite{SamplePack}, Gr\"nschlo{\ss}'s website \cite{GruWeb}, the Magic Point Shop \cite{NuyWeb}, R \cite{QRNG2020}, Julia \cite{QMCJulia}, SciPy \cite{virtanen2020scipy}, PyTorch \cite{paszke2019pytorch}, and TensorFlow \cite{tfqfQMC2021a}, and MatBuilder \cite{paulin2022}.  Joe and Kuo

@@
